Improving Software Maintainability through Automated Refactoring of Duplicate Code

### 2020-01-10 ecoop/paper.tex
Updates from Overleaf
Abstract

\title{Improving Software Maintainability through Automated Refactoring of Code Clones}

@@

We address this shortcoming by first analyzing what preconditions apply to be able to automatically refactor clones. We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them. We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system. Based on these results, one could decide which clones would improve system design if refactored. We evaluate our approach over a large corpus of open-source Java projects.

We identify the factors of interest characterizing the impact on the maintainability of automatically applied refactorings. We find that the biggest influencing factor is token volume. We define token volume as the combined number of tokens in all clone instances in a clone class. The majority of duplicates with a token volume of 63 or more tokens improve maintainability when refactored. The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones requiring more than two external parameters decrease maintainability.
\end{abstract}

>>>>

\title{Improving Software Maintainability through Automated Refactoring of Duplicate Code}

@@

We address this shortcoming by first analyzing what preconditions apply to be able to automatically refactor clones. We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them using the ``Extract Method'' refactoring technique. We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system. Based on these results, one could decide which clones would improve system design if refactored. We evaluate our approach over a large corpus of open-source Java projects.

We identify the factors of interest characterizing the impact on the maintainability of automatically applied refactorings. We find that the biggest influencing factor is the size of the clone. The majority of duplicates larger than 63 tokens improve maintainability when refactored. The amount of external data that needs to be passed to the extracted method is the other important factor: the majority of extracted methods requiring more than two parameters decrease maintainability.
\end{abstract}
